Bayesian Data Analysis - Rough Draft

### 2023-11-29 Lahman Analysis/Formal Analysis/Draft 1.qmd
Randomly Selected Players for Formal
Randomly selected 500/657 players that met the qualifying criteria in the Formal analysis

#Calculated each players HR proportion "p"
Batting <- Batting %>% 
  mutate(p = HR / AB, .after=AB)
```

@@

In this model, we say that the $HR$'s of player $n$ are binomialy distriubted with number of trials for player $n$ are $AB$. The probability of success (hitting a HR) denoted as $p$. Furthermore, we measure $p$ on the logistic scale. We note here that $p$ changes due to a variety of factors. First, we noticed in the data that most hitters hit a HR in about 3 out of every 100 AB's (REFERENCE TO FIGURE WHICH SHOWS AVERAGE HR PER AB IN MLB). Thus, we assume that the underlying probabilty of any player in the MLB for hitting a HR is about -3.5 on the logit scale, or 0.03 on the standard probability scale.

@@

```{r}
#| label: fig-RunsByYear

@@

```{r}
#| label: fig-HR.By.Age.All

@@

```{r}
#| label: fig-HR.By.Age.20to40

>>>>

#Calculated each players HR proportion "p"
Batting <- Batting %>% 
  mutate(p = HR / AB, .after=AB)
#You can see this for yourself too, but there are 657 players in this dataframe now
```

```{r}
#Choose 500 players at random to consider
#If this doesn't take too long, then we can come back later and change this to possibly consider all players. Or just widen the initial time-frame considered and do 1000 players

set.seed(500)

N_player <- Batting %>% 
  distinct(playerID) %>% 
  pull(playerID) %>% 
  sample(size=500, replace=FALSE)
```

```{r}
#Make a dataframe that only keeps the 500 players
Samp_Batting <- Batting %>% 
  filter(playerID %in% N_player)

head(Samp_Batting)
#If curious, this seed and selection covers all years. So, it should be able to handle the year-to-year effects
```

@@

In this model, we say that the $HR$'s of player $n$ are binomialy distributed with number of trials for player $n$ are $AB$. The probability of success (hitting a HR) denoted as $p$. Furthermore, we measure $p$ on the logistic scale. We note here that $p$ changes due to a variety of factors. First, we noticed in the data that most hitters hit a HR in about 3 out of every 100 AB's (REFERENCE TO FIGURE WHICH SHOWS AVERAGE HR PER AB IN MLB). Thus, we assume that the underlying probability of any player in the MLB for hitting a HR is about -3.5 on the logit scale, or 0.03 on the standard probability scale.

@@

```{r}
#| label: fig-RunsByYear
#| fig-cap: "Cumulative Runs Scored in MLB by Year"

@@

```{r}
#| label: fig-HR.By.Age.All
#| fig-cap: "Proportion of Home Runs per At-Bat by Age"

@@

```{r}
#| label: fig-HR.By.Age.20to40
#| fig-cap: "Proportion of Home Runs per At-Bat by Age"
